Operation Mode Study in Cloud Manufacturing Ecosystem

### 2016-09-13 design.tex
modify before the submission

% !TEX root = Eco-Model.tex
\section{Design of the ecosystem} % (fold)
\label{sec:design_of_the_ecosystem}
% \subsection{Preliminaries} % (fold)
% \label{sub:preliminaries}
Before introducing the design of the ecosystem, we specify some basic definitions:
\begin{compactitem}
	\item Provider: the individual who provides resource;
	\item Resource: the basic task process object with renewable capacity and unique type;
	\item Demander: the individual who publishes orders that contain bunch of tasks;
	\item Order: the task bundle like a project;
	\item Task: the basic object that needs to be processed with resource-type cooperation;
	\item Task-part: virtual resource-type segmentation unit of one task;
	\item Product: the perform result of a task;
    \item Service-call: the basic object that needs to be processed with both resource-type and resource-capacity cooperation;
    \item Job: the generalization of task and service-call;
    \item Service: the perform result of a service-call, a group of tasks;
    \item Machine: the generalization of resource and service;
	\item Platform: the place where individuals interact with others;
    \item Resource-type cooperation: resource in specific type to process a job simultaneously;
    \item Resource-capacity cooperation: part of resources in same type to process a service-call simultaneously.
\end{compactitem}

With the cloud manufacturing platform operating, demanders publish orders while providers provide resources, then they make decisions to  arrange the resources to perform tasks that decomposed from order. Most recent researchers e.g. Wu et al. \cite{Wu2013}, describe this operation procedure in cloud manufacturing as a tri-group user model that contains:\begin{inparaenum}[1)]
\item users/customers,
\item application providers and
\item physical resource providers.
\end{inparaenum}
Inspired by this model, we design the original operation mode shown in \autoref{fig:originmode} as the basis.
In this mode, individual executes activities that interact with others depicted by object flow(full lines) and information flow(dashed lines). A single order can be described by an activity-on-node(AON) network where the node represent the task and the arc the precedence relation. Each task needs to be performed with resource-type cooperation as listed in \autoref{tab:simplejobconfiguration}, and the selected resource cannot start to process the task until all of other selected resources are ready, what each resource actually processes is the task-part as show in \autoref{fig:simplejoblist}, we call the task-part is \textbf{active} when being processed, \textbf{semi-active} when selected resource is waiting as shadow in \autoref{fig:simplejoblist}, \textbf{inactive} when this part is just assigned to the job queue. Product, the performance result after the processing and assembly procedure, will be delivered to demander, then demander change the rank value of the selected resource owners according to the review of the product.

@@

@@

% \vspace{-2.5em}
% subsubsection assumptions_nomenclature (end)
\subsection{Master plan for original and extended modes} % (fold)
\label{ssub:master_plam}
In original mode, a single \textbf{order} consists of a set $\mathcal{T}_i = \left\{ t_{i1},t_{i2},\dots\right\}$ of tasks, the tasks are interrelated by kinds of constraints. First, precedence constraints force \textbf{task} $t_{ij}$ not to be started before all its immediate predecessors $\mathcal{P}_{ij}$. Second, performing the tasks requires resources with limited capacities. Third, resources cooperation requires all the task-parts in active status.
A single \textbf{resource}($mr_k$) belongs to only one type. While being processed, task $t_{ij}$ requires $q_{\alpha,ij}$ units capacity of the resources with each type $\alpha\in\mathcal{A}_{ij}$ during every period of its non-preemptable duration $p_{ij}$. Each resource $mr_k$ has a limited capacity $C_{k,\tau}$ and available capacity $A_{k,\tau}$ at any point in time $\tau$. This plan is much like the settings in RCPSP\cite{Kolisch1999} except that the task here need to be processed with resource cooperation.

The relation of proposed extended modes is shown in \autoref{fig:modes},
\begin{figure}[htbp]
    \centering
    \resizebox{\textwidth}{!}{\input{figures/modes}}
    \caption{Three Extended modes}
    \label{fig:modes}
\end{figure}
incubation and outsourcing mode are options for provider, while metabolism mode is option for platform operator, and the outsourcing mode can only be applied if incubation mode is applied because only the task that processed by service can be outsourced.

@@

\subsection{Incubation mode} % (fold)
\label{sub:incubation_mode}
Incubation mode is one extension for the original mode, the purpose of this mode is to remove the cooperation and assembly procedure in advance by gathering types of resources with certain quota into manufacturing service, which will be incubated as shown in incubation part of \autoref{fig:modes}.
% \begin{figure}[htbp]
%     \centering
%     \resizebox{0.7\textwidth}{!}{\input{figures/service-incubate}}
%     \caption{Incubation mode}
%     \label{fig:serviceincubatemode}
% \end{figure}
\begin{figure}[htbp]
    \centering
    \scriptsize
    \resizebox{.65\textwidth}{!}{\input{figures/service}}
    \caption{Service incubation illustration}
    \label{fig:servicefigure}
\end{figure}
After the finish of task-part, provider record the resource configuration as task frequency, when the frequency value reached some point, provider will decide to incubate such a task-specified service for the future performance. For example, if task $job_1$ in \autoref{tab:simplejobconfiguration} was finished, the first thing of incubation for the resource provider is to publish a job named \textbf{service-call} ($job_6$), which is similar to task except for the capacity dominance feature , which means capacity of selected resource will not be restored after the processing. The process result of one service-call is manufacturing \textbf{service} as shown in \autoref{fig:servicefigure}, which is actually a set of resources that may come from selected providers in the system, it's possible for more than one resources in a same type to make contributions to the incubation of one service. No more cooperation and assembly procedure are one pro of service, and product quality will no longer be restricted to the worst quality of resources for the complementary effect, while one con of service include that service can only perform specified task.
Now we can generalize task and service-call into \textbf{job}, resource and service into \textbf{machine} for the follow discuss.

>>>>

% !TEX root = Eco-Model.tex
\section{Design of the ecosystem} % (fold)
\label{sec:design_of_the_ecosystem}
% \subsection{Preliminaries} % (fold)
% \label{sub:preliminaries}
Before introducing the design of the ecosystem, we specify some basic definitions:
\begin{compactitem}
	\item Provider: the individual who provides resource;
	\item Resource: the basic task process object with renewable capacity and unique type;
	\item Demander: the individual who publishes orders that contain bunch of tasks;
	\item Order: the task bundle like a project;
	\item Task: the basic object that needs to be processed with resource-type cooperation;
	\item Task-part: virtual resource-type segmentation unit of one task as squares in \autoref{fig:scheduleChart};
	\item Product: the perform result of a task;
    \item Service-call: the basic object that needs to be processed with both resource-type and resource-capacity cooperation;
    \item Job: the generalization of task and service-call;
    \item Service: the perform result of a service-call, a group of tasks;
    \item Machine: the generalization of resource and service;
	\item Platform: the place where individuals interact with others;
    \item Resource-type cooperation: resource in specific type to process a job simultaneously;
    \item Resource-capacity cooperation: part of resources in same type to process a service-call simultaneously as in \autoref{fig:servicefigure}.
\end{compactitem}

Platform is the cradle of the ecosystem and the incubator for manufacturing service, with the cloud manufacturing platform operating, demanders publish orders while providers provide resources, then they make decisions to  arrange the resources to perform tasks that decomposed from order. Most recent researchers e.g. Wu et al. \cite{Wu2013}, describe this operation procedure in cloud manufacturing as a tri-group user model that contains:\begin{inparaenum}[1)]
\item users/customers,
\item application providers and
\item physical resource providers.
\end{inparaenum}
Inspired by this model, we design the original operation mode shown in \autoref{fig:originmode} as the basis.
In this mode, individual executes activities that interact with others depicted by object flow (full lines) and information flow (dashed lines). A single order can be described by an activity-on-node (AON) network where the node represent the task and the arc the precedence relation. Each task needs to be performed with resource-type cooperation as listed in \autoref{tab:simplejobconfiguration}, and the selected resource cannot start to process the task until all of other selected resources are ready, what each resource actually processes is the task-part and we call the task-part is \textbf{active} when being processed, \textbf{semi-active} when selected resource is waiting as shadow in \autoref{fig:scheduleChart}, \textbf{inactive} when this part is just assigned to the job queue. Product, the performance result after the processing and assembly procedure, will be delivered to demander, then demander change the rank value of the selected resource owners according to the review of the product.

@@

\item Operate of the ecosystem starts from the very beginning that no demander or provider is registered;

@@

% \vspace{-2.5em}
% subsubsection assumptions_nomenclature (end)
\subsection{Master plan for original and extended modes} % (fold)
\label{ssub:master_plam}
In original mode, operating of ecosystem begins with void, then there comes the registration of provider and demander. A single \textbf{order} consists of a set $\mathcal{T}_i = \left\{ t_{i1},t_{i2},\dots\right\}$ of tasks, the tasks are interrelated by kinds of constraints. First, precedence constraints force \textbf{task} $t_{ij}$ not to be started before all its immediate predecessors $\mathcal{P}_{ij}$. Second, performing the tasks requires resources with limited capacities. Third, resources cooperation requires all the task-parts in active status.
A single \textbf{resource}($mr_k$) belongs to only one type. While being processed, task $t_{ij}$ requires $q_{\alpha,ij}$ units capacity of the resources with each type $\alpha\in\mathcal{A}_{ij}$ during every period of its non-preemptable duration $p_{ij}$. Each resource $mr_k$ has a limited capacity $C_{k,\tau}$ and available capacity $A_{k,\tau}$ at any point in time $\tau$. This plan is much like the settings in RCPSP\cite{Kolisch1999} except that the task here need to be processed with resource cooperation.

The life cycle management of resource contains its vicissitude, which is the design basis of proposed extended modes \autoref{fig:modes}.
\begin{figure}[htbp]
    \centering
    \resizebox{\textwidth}{!}{\input{figures/modes}}
    \caption{Three Extended modes}
    \label{fig:modes}
\end{figure}
Incubation and outsourcing mode are options for provider, while metabolism mode is option for platform operator, and the outsourcing mode can only be applied if incubation mode is applied because only the task that processed by service can be outsourced.

@@

\subsection{Incubation mode} % (fold)
\label{sub:incubation_mode}
Incubation mode is one extension for the original mode, the purpose of this mode is to remove the cooperation and assembly procedure in advance by gathering types of resources with certain quota into manufacturing service, which will be incubated as shown in incubation part of \autoref{fig:modes}.
% \begin{figure}[htbp]
%     \centering
%     \resizebox{0.7\textwidth}{!}{\input{figures/service-incubate}}
%     \caption{Incubation mode}
%     \label{fig:serviceincubatemode}
% \end{figure}
\begin{figure}[htbp]
    \centering
    \scriptsize
    \resizebox{.65\textwidth}{!}{\input{figures/service}}
    \caption{Service incubation from $job_7$ in \autoref{tab:simplejobconfiguration}}
    \label{fig:servicefigure}
\end{figure}
After the finish of task-part, provider record the resource configuration as task frequency, when the frequency value reached some point, provider will decide to incubate such a task-specified service for the future performance. As the example in \autoref{fig:servicefigure}, if task $job_1$ in \autoref{tab:simplejobconfiguration} was finished, the first thing of incubation for the resource provider is to publish a job named \textbf{service-call} ($job_7$), which is similar to task except for the capacity dominance feature , which means capacity of selected resource will not be restored after the processing. The process result of one service-call is manufacturing \textbf{service} as shown in \autoref{fig:servicefigure}, which is actually a set of resources that may come from selected providers in the system, it's possible for more than one resources in a same type to make contributions to the incubation of one service. No more cooperation and assembly procedure are one pro of service, and product quality will no longer be restricted to the worst quality of resources for the complementary effect, while one con of service include that service can only perform specified task.
Now we can generalize task and service-call into \textbf{job}, resource and service into \textbf{machine} for the follow discuss.

### 2016-09-13 head.tex
modify before the submission

\author[add1]{Shengkai Chen}
\author[add2,add1]{Shuiliang Fang\corref{cor1}}
\author[add2,add1]{Tao Peng}
% \ead{me_fangsl@zju.edu.cn}
% \address[label1]{ZJU}
% \address[label1]{Address One}
\address[add2]{The State Key Laboratory of Fluid Power Transmission and Control, College of Mechanical Engineering, Zhejiang University, Hangzhou, 310027, China}
\address[add1]{Key Laboratory of Advanced Manufacturing Technology of Zhejiang Province, College of Mechanical Engineering, Zhejiang University, Hangzhou , 310027, China}
% \author[a,b,*]{Third Author}

@@

\begin{abstract}
In cloud manufacturing, platform operator is able to manage distributed massive manufacturing resources for manufacturing business.
Cloud manufacturing ecosystem has more complicated relationship among individuals than that in existing manufacturing system, every individual makes decisions depend on enriched information. In this paper, an original operation mode with three extensions namely incubation, outsourcing and metabolism mode are proposed. We designed an agent-based simulation model and the validation experiment result shows platform have: 1) shorter job queue length and lower resource idle rate with incubation mode; 2) a little shorter job queue length and fewer amount of registered resource with outsourcing mode; 3) the fewest amount of registered resource but a little higher resource idle rate with metabolism mode.

>>>>

\author[add1]{Shengkai Chen}
\author[add2,add1]{Shuiliang Fang\corref{cor1}}
\author[add2]{Tao Peng}
\author[add2]{Renzhong Tang}
% \ead{me_fangsl@zju.edu.cn}
% \address[label1]{ZJU}
% \address[label1]{Address One}
\address[add2]{The State Key Laboratory of Fluid Power Transmission and Control, College of Mechanical Engineering, Zhejiang University, Hangzhou, 310027, China}
\address[add1]{Key Laboratory of Advanced Manufacturing Technology of Zhejiang Province, College of Mechanical Engineering, Zhejiang University, Hangzhou , 310027, China}
% \author[a,b,*]{Third Author}

@@

\begin{abstract}
With cloud manufacturing, platform operator is able to manage distributed massive manufacturing resources for manufacturing business.
Ecosystem of cloud manufacturing has more complicated relationship among individuals than that in existing manufacturing system, every individual makes decisions depend on enriched information, which will help optimize for the overall industry. In this paper, an original operation mode with three extensions are proposed to describe the life cycle vicissitude of each resource. We designed an agent-based simulation model and the validation experiment result shows platform have: 1) shorter job queue length and lower resource idle rate with incubation mode; 2) a little shorter job queue length and fewer amount of registered resource with outsourcing mode; 3) the fewest amount of registered resource but a little higher resource idle rate with metabolism mode.

### 2016-09-13 intro.tex
modify before the submission

% !TEX root = Eco-Model.tex
\section{Introduction}
The relationship among entities in a cloud manufacturing system become more complicated than that in existing manufacturing systems, since the integration of advanced technologies makes it possible for individual to make decisions depend on enriched information. Demanders prefer high quality of performance, while providers prefer high use rate of resource. A cloud platform operator prefers a fewer amount of registered resource when dealing with almost arriving needs for an easier maintenance. These preferences stimulate the emergence of good service pattern that will lead to the emergence operation mode in the cloud manufacturing ecosystem. Hence, it's important to identify a suitable operation mode to meet most of individuals' preference.

>>>>

% !TEX root = Eco-Model.tex
\section{Introduction}
The relationship among entities in a cloud manufacturing system become more complicated than that in existing manufacturing systems, since the integration of advanced technologies makes it possible for individual to make decisions depend on enriched information. Demanders prefer high quality of performance, while providers prefer high use rate of resource. A cloud platform operator prefers a suitable amount of registered resources to satisfy the needs of the market and for an easier life cycle management of resources. These preferences stimulate the emergence of good service pattern that will lead to the emergence operation mode in the cloud manufacturing ecosystem. Hence, it's important to identify a suitable operation mode to meet most of individuals' preference and to optimize the resource management.

### 2016-09-13 result.tex
modify before the submission

\subsection{Experiments} % (fold)
\label{ssub:case_design}
We design experiments to repeatedly simulate the operating of ecosystem with 6 different mode combinations in \autoref{tab:grouping} group by group, which are the prototypes of feasible cloud manufacturing operating modes. Every single simulation goes with the main flow as show in \autoref{fig:originmode}. We use  RanGen \cite{Demeulemeester2003} to generate dataset in the well-known Patterson format as the the continuously arriving order for the simulation input, related parameter settings are listed in \autoref{tab:generalparameter}.
\begin{table}[htbp]
  \centering
  \scriptsize
  \caption{Order generating parameters setting}
    \begin{tabular}{cccccccccc}
    \toprule
    \textbf{$n_a$} & \textbf{OS} & \textbf{CI} & \textbf{$n_r$} & \textbf{RF} & \textbf{RC} & \textbf{$\lambda_d$} &\textbf{$\lambda_p$} & \textbf{$C_{k,0}$}\\
    \midrule
     10  &   0.3    &  [2,3]     &   12     &  0.3     &   0.5  & 0.2 & 0.3  & [20,30] \\
    \bottomrule
    \end{tabular}%
    {\footnotetext{\tiny The meaning of the first 5 parameters are defined in \cite{Demeulemeester2003}, $\lambda$ is the parameters of the arrival of user in simulation, $C_{k,0}$ is the initial capacity for $mr_k$}
    }
  \label{tab:generalparameter}%
\end{table}%

>>>>

\subsection{Experiments} % (fold)
\label{ssub:case_design}
We design experiments to repeatedly simulate the operating of ecosystem from the very beginning with mode combinations in \autoref{tab:grouping} group by group, which are the prototypes of feasible cloud manufacturing operating modes. Every single simulation goes with the main flow as show in \autoref{fig:originmode}. We use  RanGen \cite{Demeulemeester2003} to generate dataset in the well-known Patterson format as the the continuously arriving order for the simulation input, related parameter settings are listed in \autoref{tab:generalparameter}.
\begin{table}[htbp]
  \centering
  \scriptsize
  \caption{Order generating parameters setting}
    \begin{tabular}{cccccccccc}
    \toprule
    \textbf{$n_a$} & \textbf{OS} & \textbf{CI} & \textbf{$n_r$} & \textbf{RF} & \textbf{RC} & \textbf{$\lambda_d$} &\textbf{$\lambda_p$} & \textbf{$C_{k,0}$}\\
    \midrule
     10  &   0.3    &  [2,3]     &   12     &  0.3     &   0.5  & 0.2 & 0.3  & [20,30] \\
    \bottomrule
    \end{tabular}%
    {\footnotetext{\tiny The meaning of the first 5 parameters are defined in \cite{Demeulemeester2003}, $\lambda$ is the parameters of the arrival of user in simulation, $C_{k,0}$ is the initial capacity for $mr_k$}
    }
  \label{tab:generalparameter}%
\end{table}%
